Community-Conditioned Language Models

### 2020-11-20 paper/paper.tex
address some todos

As a quantitative assessment, we compare the CCLM-learned community
embedding with the community embedding created by \citet{Kumar2018},
who generated them from the message-community co-occurence matrix,
using data which spans January 2014 to April 2017. We refer the reader
to \citet{Kumar2018}
\jp{What they say they do (sec 6.2) More formally, we train user and community embeddings basedon the bipartite multigraph between users and communities, whereone user-community edge,(ui,cj), exists in the graph for each timea user,ui, posts on community,cj. Adapting the approach used ina number of recent successful works [27,53,62], we learn user andcommunity embeddings,ui∈Rd,cj∈Rd, from this graph using anegative-sampling optimization algorithm
}
for details, but the important point is that no linguistic
information is used to create these embeddings: they only depend on
whether and how much a given user participates in a given
community. In sharp contrasts, CCLM community embeddings depend in no
way on which user is the author of any given message: we only use the
contents of messages, not authorship data. 
%
We correlate the pairwise cosine similarity of the
CCLM embeddings with the same metric on the membership embedding,
restricted to the 46 communities chosen for our study
(\cref{fig:pairwise-comm-sim}).

@@

With indiscernibility values of 1.5 to 3.5 (out of a maximum of 46)\jp{Inconsistent with data; to revisit},
we find that CCLMs can be used to recognize communities based on
latent bayesian classification \ref{hyp:LMCC-works}. Even the most
generic communities appear to exhibit fairly specific linguistic
patterns. Furthermore, these patterns are just as recognizable by LSTM
or Transformer models, when properly configured and trained.

We cannot exclude a correlation (\cref{tab:cclm_lmcc_ppl}) between the perplexity of the
% \bn{I'm not sure if we can make this claim or not with the Ppl-Ppl correlations. However, given that *all* of them have positive correlation, even though the p-values are somewhat higher than .1 maybe we can?}
CCLM and the indiscernibility of the corresponding community
\ref{hyp:rich-harder-to-identify}. Because we have relatively few,
and only large communities in our test set, it is difficult to
provide a conclusive answer, but this kind of correlation would suggest that
community-specific complexity can be partially attributed to using
more varied patterns. However, even the most complex communities
(perplexity per word above 100) have an indiscernibility of about 3
(out of a maximum of 46), so they retain fairly specific patterns:
they are not simply an even mixture of the kind of comments found in
other communities.

>>>>

As a quantitative assessment, we compare the CCLM-learned community
embedding with the community embedding created by \citet{Kumar2018},
who generated them using using a negative-sampling optimization
algorithm and the message-community co-occurence matrix as ground
truth, using data which spans January 2014 to April 2017.
We refer the reader
to \citet{Kumar2018}
for details, but the important point is that no linguistic
information is used to create these embeddings: they only depend on
whether a given user participates in a given
community. In sharp contrasts, CCLM community embeddings depend in no
way on which user is the author of any given message: we only use the
contents of messages, not authorship data.
%
We correlate the pairwise cosine similarity of the
CCLM embeddings with the same metric on the membership embedding,
restricted to the 46 communities chosen for our study
(\cref{fig:pairwise-comm-sim}).

@@

With indiscernibility values evenly ranging over the whole possible
range (0 to 1), we find that CCLMs can be used to recognize certain
communities based on latent bayesian classification
\ref{hyp:LMCC-works}, but not all.  If generic communities exhibit
distinctive linguistic patterns, none of our model is able to discern
them. In contrast, the distinctive patterns of narrow-topic
communities are just as recognizable by all our LSTM and Transformer
models.

We cannot exclude a correlation (\cref{tab:cclm_lmcc_ppl}) between the perplexity of the
% \bn{I'm not sure if we can make this claim or not with the Ppl-Ppl correlations. However, given that *all* of them have positive correlation, even though the p-values are somewhat higher than .1 maybe we can?}
CCLM and the indiscernibility of the corresponding community
\ref{hyp:rich-harder-to-identify}. Because we have relatively few,
and only large communities in our test set, it is difficult to
provide a conclusive answer, but this kind of correlation would suggest that
community-specific complexity can be partially attributed to using
more varied patterns. However, even the most complex communities
(perplexity per word above 100) have an indiscernibility of about 3
(out of a maximum of 46)\jp{make consistent with data}, so they retain fairly specific patterns:
they are not simply an even mixture of the kind of comments found in
other communities.
